### 2017-10-10 Gruba/07-rela.tex

There have been established work of extracting user interests.
\cite{IEEEexample:journals/fcsc/LiuCS12} mined the user interests by exploring keywords of blogs with the aid of word frequency and machine translation.  
\cite{IEEEexample:conf/webi/XuLXY11} proposed a method of extending the topic model to obtain use interests. 
Also, \cite{IEEEexample:conf/and/MichelsonM10} used a knowledge base and \cite{IEEEexample:conf/icde/FengW14} provided a solution of using hashtag for interest analysis. 
\cite{IEEEexample:conf/wikis/LimD13} summarized user interest by exploring the mentioned celebrities; 
Similarly, \cite{IEEEexample:conf/recsys/BhattacharyaZGGG14} leveraged the followed experts to result interest characteristics.
Unlike the existed solutions, \sys{} employs a cell lexicon to properly express user interest in which Twitter-LDA \cite{IEEEexample:zhao2011comparing} and TF-IDF \refe{} are employed.

>>>>

There have been established work of extracting user interests.
\cite{IEEEexample:journals/fcsc/LiuCS12} mined the user interests by exploring keywords of blogs with the aid of word frequency and machine translation.
\cite{IEEEexample:conf/webi/XuLXY11} proposed a method of extending the topic model to obtain use interests.
Also, \cite{IEEEexample:conf/and/MichelsonM10} used a knowledge base and \cite{IEEEexample:conf/icde/FengW14} provided a solution of using hashtag for interest analysis.
\cite{IEEEexample:conf/wikis/LimD13} summarized user interest by exploring the mentioned celebrities;
Similarly, \cite{IEEEexample:conf/recsys/BhattacharyaZGGG14} leveraged the followed experts to result interest characteristics.
Unlike the existed solutions, \sys{} employs a cell lexicon to properly express user interest in which Twitter-LDA \cite{IEEEexample:zhao2011comparing} and TF-IDF are employed.
